Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-06-02 paper.tex
Update on Overleaf.

Most operating system kernels are predominantly written in the C programming language with bits of
assembly. C has been favored for its low-level capabilities and performance efficiency, crucial for
kernel development. However, the inherent lack of memory safety in C has led to numerous security
vulnerabilities, including buffer overflows and use-after-free errors, which have plagued operation
system development for decades~\cite{noauthor_undated-bf}. Addressing these vulnerabilities is
paramount to enhancing the security and reliability of all operating systems.

Rust, a systems programming language developed by Mozilla, has garnered significant attention for
its strong emphasis on memory safety without sacrificing performance. Rust's ownership model and its
compile-time checks effectively prevent common programming errors that lead to security
vulnerabilities. What makes Rust unique is the fact that it accomplishes these tasks without the use
of a garbage collector, making it an ideal candidate for kernel development where safety and
performance are critical.

>>>>

Most operating system kernels are predominantly written in the C programming language with bits of
assembly. C has been favored for its low-level capabilities and performance efficiency, crucial for
kernel development. However, the inherent lack of memory safety in C has led to numerous security
vulnerabilities, including buffer overflows and use-after-free errors, which have plagued operation
system development for decades~\cite{noauthor_2019-bf}. Addressing these vulnerabilities is
paramount to enhancing the security and reliability of all operating systems.

Rust, a systems programming language developed by Mozilla, has garnered significant attention for
its strong emphasis on memory safety without sacrificing performance. Rust's ownership model and its
compile-time checks effectively prevent common programming errors that lead to security
vulnerabilities. What makes Rust unique is the fact that it accomplishes these tasks without the use
of a garbage collector, making it an ideal candidate for kernel development where safety and
performance are critical~\cite{noauthor_2024-id}.
